### 2022-05-14 manuscript.Rmd
Update contributions

M.A.S. conceived, designed, and obtained funding for the study.

A.E., S.K., and A.K. designed and executed the search strategy, performed study selection and screening procedures, managed the database of search results and performed data analysis in consultation with M.A.S.

A.E. and M.A.S. wrote the manuscript with feedback from S.K. and A.K.

>>>>

\noindent M.A.S. conceived, designed, and obtained funding for the study.

\noindent A.E., S.K., and A.-S.K. designed and executed the search and selection strategies, performed data analysis, conducted robustness checks, and visualized the results in consultation with M.A.S.

\noindent A.E. and M.A.S. wrote the manuscript with additional input from S.K. and A.-S.K.
